Designing an Indoor Guidance System for the Visually Impaired

### 2018-11-02 paper.tex
Starting edits, added new control loop figure

\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely safely navigate towards their desired destination or find an object in an unknown and dynamic environment. One requirement for this is the ability for a device to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.

In this paper we discuss the first steps we've taken into implementing such a system. Specifically, we implemented a system with the capability to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.

This work's main contribution is the design of a guidance system and MDP that can drive a user to point a mobile device's camera towards a given point in space in and find a target object. The interface is pictured in Figure~\ref{fig:system-screenshot}. We also present and discuss preliminary experimental results to show how effective the system is at finding a target.

The next section discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system and MDP\@. Then we discuss the experiment and present its results, after which we conclude the paper and discuss the project's next steps.

\section{\uppercase{Previous Work}}

\noindent Assistive vision and guidance for the VI is an active and diverse field of study. In recent years, the increase in mobile processing power and computer vision improvements have led to researchers investigating using a cellphone camera to augment or enhance a user's vision and help them find objects or another point of interest. Earlier attempts at the problem involved placing special markers or barcodes, encoded with information about an object or the area, around an environment, which the user then scans with a cellphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. This device then uses some feedback mode, e.g.\ Braille and sound, to guide the user towards the target. The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user. Furthermore, these passive systems rely on the user scanning the marker in the first place; something that can be made more complicated with markers degrading over time, changing ambient lighting, different viewing angles and marker occlusion.

Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}. The system described~\cite{schauerte2012assistive} uses a combination of Scale Invariant Feature Transform (SIFT)~\cite{lowe1999object} and Speeded Up Robust Features (SURF)~\cite{bay2006surf} to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions. This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place. The paper also does not report on any performance metrics. In~\cite{bigham2010vizwiz}, the authors discuss their VizWiz system that offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user. The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions. However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander. Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.

As shown here, much research has been performed on object recognition and guidance towards an object once detected. However, work on active object search is harder to come by. Therefore, in this work we attempt to implement a system that uses active vision~\cite{aloimonos1988active} to guide a user towards an out-of-view target object by using the history of past object observations made during the search. With this, we hope to make the searching process less random and move towards a more natural search object searching process.

\section{\uppercase{Guidance System Design}}

@@

\section{\uppercase{Experiments}}

@@

\section{\uppercase{Future Work and Conclusion}}

>>>>

\noindent We are designing an indoor navigation system targeted towards enabling blind and visually impaired (VI) users to safely navigate towards their desired destination or find an object in an unknown and dynamic environment, expanding upon ideas originally proposed in~\cite{bellotto2013}. The proposed system implements ideas from the active vision field and places a human in the control loop. This control loop, pictured in Figure~\ref{fig:control-loop}, comprises of a controller, $K$, that is given a reference signal (the desired objects in this case) that generates a control signal, $u$, which a human, $H$, uses to manipulate a sensor, $P$, to gather more information on the environment and move closer to the target object. %The goal of this system is to automatically make sense of the user's surroundings and determine the optimal route to get to the final destination based on what the user/camera sees, thereby roughly emulating a normally sighted user's navigation strategy in an unknown environment.

\begin{figure}
  \includegraphics[width=0.4\textwidth]{figures/control_loop.png}
  \caption{The control }\label{fig:control-loop}
\end{figure}

In this paper we discuss the first steps we've taken into implementing the control-block, $K$, from Figure~\ref{fig:control-loop}. The goal of this system is to understand the user's surroundings and determine what the next best course of action is to reach the target location, based on what the system is currently seeing and what it has seen in the past. We used a Markov Decision Process (MDP)~\cite{bellman1957markovian} to produce a so-called policy that defines the optimal action, $a$, our agent (the guidance system in this case) takes when it is in some state $s$.

This work's main contribution is the design of a guidance system and MDP that can drive a user to point a mobile device's camera towards a given point in space in and find a target object. We also present and discuss preliminary experimental results to show how effective the system is at finding a target.

Section~\ref{sec:previous-work} discusses other relevant work done in this field, followed by a detailed discussion on the design of the guidance system, human-control module and MDP\@ in Sections~\ref{sec:system-design} and~\ref{sec:controller-design}. Then we discuss the experiment and present its results in Section~\ref{sec:experiments}, after which we conclude the paper and discuss the project's next steps in Section~\ref{sec:conclusion}.

\section{\uppercase{Previous Work}}\label{sec:previous-work}

\noindent Assistive vision and guidance for the VI is an active and diverse field of study. In recent years, the increase in mobile processing power and computer vision improvements have led to researchers investigating using a cellphone camera to augment or enhance a user's vision and help them find objects or another point of interest. Earlier attempts at the problem involved placing special markers or barcodes, encoded with information about an object or the area, around an environment, which the user then scans with a cellphone or similar mobile device~\cite{gude2013blind,iannizzotto2005badge3d,manduchi2012mobile}. This device then uses some feedback mode, e.g.\ Braille and sound, to guide the user towards the target. %The major drawbacks to this approach is the significant upfront effort required to augment entire areas with markers to a point where the system will be useful to a VI user. Furthermore, these passive systems rely on the user scanning the marker in the first place; something that can be made more complicated with markers degrading over time, changing ambient lighting, different viewing angles and marker occlusion.

Another approach is to discard tags completely and rely on computer vision to perform the object detection, something that has become more plausible with recent improvements to feature detectors and deep networks~\cite{huang2017speed,redmon2016you}. The system described~\cite{schauerte2012assistive} uses a combination of SIFT and SURF to detect known objects when they are in the camera's view and guide the user to them using sonified guidance instructions. This system is more flexible than the tag-based ones, but have the same drawback of being passive and rely on chance for the user to place the object within the camera's view in the first place. The paper also does not report on any performance metrics. In~\cite{bigham2010vizwiz}, the authors discuss their VizWiz system that offloads the object recognition tasks to an Amazon Mechanical Turk worker that then provides feedback on where the object of interest is located relative to the user. The VizWiz has the advantage of being fairly robust and is able to classify a great deal of objects with little effort from the user and can provide natural, human-generated and curated directions. However, this approach does not address the issue of enhancing user independence, since the user is now beholden to an online worker instead of a relative, friend or bystander. Furthermore, a good internet connection is required on the device, perhaps limiting use in some poor-reception areas.

As shown here, much research has been performed on object recognition and guidance towards an object once detected. However, work on active object search is harder to come by. Therefore, in this work we attempt to implement an active vision~\cite{aloimonos1988active, bellotto2013, lock2017portable} that can guide a user towards an out-of-view target object by using prior knowledge of the spatial distribution of objects within an indoor environment and the history of past object observations made during the search. With this, we hope to make the searching process less random and move towards a more natural search object searching process to the benefit of the VI.

\section{\uppercase{Active Vision System Design}}\label{sec:system-design}

\section{\uppercase{Human-control Module}}\label{sec:controller-design}

@@

\section{\uppercase{Experiments}}]\label{sec:experiments}

@@

\section{\uppercase{Future Work and Conclusion}}\label{sec:conclusion}
